### 2021-03-14 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Detection and Mitifation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

>>>>

\section{Detection and Mitigation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

### 2021-03-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Threat Model}

\section{Examples}

\section{Math Notations}
e now discuss how to model observations ($O$), which are the direct information
that an adversary can get during the attack.

>>>>

\section{Threat Model}
We assume that an attacker shares the same hardware platform with the target.
Here are a few examples. 1) A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can start a new VM and probe the process running on the other VM.  2) In a shielding system, a malicious operating system can extract sensitive information from the protected application. 
The attacker attempts to retrieve sensitive information through address-based
side-channel attacks. The attacker has no direct access to the target's memory or cache,
but it can probe its memory or cache at each program point. In reality, the
attacker will face many possible obstacles such as the noisy observations 
of the memory or cache. However, for this project, we assume
the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
The threat model captures most cache-based and address-based side-channel attacks. 
We only consider deterministic programs and assume an attacker 
has access to the source code or binary executable of the target program.

\section{Math Notations}
We now discuss how to model observations ($O$), which are the direct information
that an adversary can get during the attack.
